Concurrent Programming with CXL

### 2020-05-20 book/paper.tex
Covered lock interface now

>>>>

\begin{figure}
\begin{code}
\begin{verbatim}
def tas(lk):
    atomic:
        result = ^lk;
        ^lk = True;
    ;
;
def lock(lk):
    while tas(lk):
        pass;
    ;
;
def unlock(lk):
    ^lk = False;
;
def Lock():
    result = False;
;
\end{verbatim}
\end{code}
\caption{The \texttt{Lock} interface in the \texttt{synch} module.}
\label{fig:locks}
\end{figure}

\begin{figure}
\begin{code}
\verbatiminput{../Lock.cxl}
\end{code}
\caption{Mutual Exclusion using the \texttt{Lock} interface of the \texttt{synch} module.}
\label{fig:lockme}
\end{figure}

Locks are probably the most popular and basic form of synchronization
in concurrent programs.  For this reason, CXL has a module called
\texttt{synch} that includes support for locks.
Figure~\ref{fig:locks} shows how they are implemented, and
Figure~\ref{fig:lockme} gives an example of how they may be used.
Notice that the module completely hides the implementation of the
lock.
